Verifying Demonstrations

### 2018-05-29 paper/protocol.tex
Changes back from footnotesize to normalsize in figures
Splits protocol section into subsections

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtest 
Outcomes.
The protocol consists of four phases: the setup, join, participation and 
submission phases.
We have several roles.
We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
identity and a cryptographic key.
We have the protesters who want to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate*}
\item We have the \emph{organizer} who will simply write a manifesto for the 
  protest and spread to others.
\item A \emph{participant} participates in the protest (and asks witnesses to 
  vouch for his presence).
\item A \emph{witness} provides proofs to participants that state the 
  participant was indeed participating and the proofs are verifiable by third 
  parties.
\end{enumerate*}
In general, there is one organizer and every protester will act as both 
participant and witness.

The setup and registration phases are the same as in Anon-Pass~\cite{AnonPass}.
We have simply adapted their description for our notation, but tried to keep 
them as similar as possible.

@@

@@

\begin{figure}
  \centering
  \footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
    key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
    \(\sk_W\) and \(\pid\).
    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
    witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of 
    \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the participant uploads the tuple \[
  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
\] for permanent storage.
\daniel{Return \(\pi'\), whatever that should be.}

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
\] for permanent storage.
\daniel{Return \(\pi''\), whatever that should be.}

>>>>

We now present \PRIVO, a protocol for securely and PRIvately Verifying PROtest 
Outcomes.
The protocol consists of five phases: the setup, join, participation, 
submission and verification phases.
The setup is described in \cref{ProtocolSetup}.
The join, participation and submission phases are described in 
\cref{ProtocolDuring}.
Finally, the verification phase is described in \cref{ProtocolVerification}.

We have several roles.
We have \iac{CA} who is responsible for a one-to-one mapping between a person's 
identity and a cryptographic key.
The \ac{CA} is only involved in the setup phase.
We also have the protesters who want to participate in a given protest.
A protester can assume three different roles:
\begin{enumerate*}
\item We have the \emph{organizer} who will simply write a manifesto for the 
  protest and spread to others.
\item A \emph{participant} participates in the protest (and asks witnesses to 
  vouch for his presence).
\item A \emph{witness} provides proofs to participants that state the 
  participant was indeed participating and the proofs are verifiable by third 
  parties.
\end{enumerate*}
In general, there is one organizer and every protester will act as both 
participant and witness.

\subsection{The setup phase}

The setup phase is only run once and is the same as in 
Anon-Pass~\cite{AnonPass}.
We have simply adapted their description for our notation, but otherwise tried 
to keep them as similar as possible.

@@

\subsection{Creating, joining, participating in a protest and submitting 
  proofs}

@@

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
    key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
    \(\sk_W\) and \(\pid\).
    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
    witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of 
    \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  %\footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the participant uploads the tuple \[
  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
\] for permanent storage.
\daniel{Return \(\pi'\), as specified as output.}

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
\] for permanent storage.
\daniel{Return \(\pi''\), as specified as output.}

\subsection{Verifying the participation count}

\dots
